\textbf{Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}

### 2023-11-21 manuscript_BiSC_outdoor_AP.tex
Updates from Overleaf

%%% --- Authors --- %%%
\author[1, 2]{Alan Domínguez}
\author[1, 3, 4]{Payam Dadvand}
\author[1]{Marta Cirach}
\author[1]{Bruno Raimbault}
\author[1]{Toni Galmes}
\author[1]{Karl Samuelsson}
\author[1, 2, 3]{Mark Nieuwenhuijsen}
\author[1, 2, 3]{Jordi Sunyer}
\author[1, 2, 3]{Xavier Basagaña}
\author[1, 3]{Ioar Rivas}

%%% --- Affiliations --- %%%
\affil[1]{Barcelona Institute for Global Health (ISGlobal), Barcelona, Spain.}
\affil[2]{Universitat Popmpeu Fabra (UPF), Barcelona, Spain.}
\affil[3]{CIBER Epidemiología y Salud Pública (CIBERESP), Madrid, Spain.}
\affil[4]{London School of Hygiene and Tropical Medicine (LSHTM), London, UK.}

@@

\begin{table}[ht]
\centering
\begin{tabular}{llllll}
\toprule
\textbf{Model} & \textbf{Pollutant} & \textbf{Dataset campaign} & \textbf{N} & \textbf{R\textsuperscript{2} (10-CV)} & \textbf{RMSE (10-CV)} \\
\midrule
\multirow{6}{*}{HM} & NO\textsubscript{2} & BiSC-home & 1232 & 0.64 & 7.48 \\
& PM\textsubscript{2.5} & BiSCAPE & 161 & 0.66 & 3.45 \\
& BC & BiSCAPE & 74 & 0.86 &  0.23 \\
& Fe & BiSCAPE & ... & ... & ... \\
& Cu & BiSCAPE & ... & ... & ... \\
& Zn & BiSCAPE & ... & ... & ... \\
\bottomrule
\end{tabular}
\caption{Descriptive caption for the table.}
\label{tab:my_label}
\end{table}

@@

>>>>

%%% --- Authors --- %%%
\author[1, 2, 3]{Alan Domínguez}
\author[1, 3, 4]{Payam Dadvand}
\author[1]{Marta Cirach}
\author[1]{Bruno Raimbault}
\author[1]{Toni Galmes}
\author[1]{Karl Samuelsson}
\author[1, 2, 3]{Mark Nieuwenhuijsen}
\author[1, 2, 3]{Jordi Sunyer}
\author[1, 2, 3]{Xavier Basagaña}
\author[1, 3]{Ioar Rivas}

%%% --- Affiliations --- %%%
\affil[1]{Barcelona Institute for Global Health (ISGlobal), Barcelona, Spain.}
\affil[2]{Universitat Pompeu Fabra (UPF), Barcelona, Spain.}
\affil[3]{CIBER Epidemiología y Salud Pública (CIBERESP), Madrid, Spain.}
\affil[4]{London School of Hygiene and Tropical Medicine (LSHTM), London, UK.}

@@

\begin{table}[ht]
\centering
\caption{Performance metric for hybrid models.}
\begin{tabular}{llllll}
\toprule
\textbf{Model} & \textbf{Pollutant} & \textbf{Dataset campaign} & \textbf{N} & \textbf{R\textsuperscript{2} (10-CV)} & \textbf{RMSE (10-CV)} \\
\midrule
\multirow{6}{*}{HM} & NO\textsubscript{2} & BiSC-hchatome & 1232 & 0.64 & 7.48 \\
& PM\textsubscript{2.5} & BiSCAPE & 161 & 0.66 & 3.45 \\
& BC & BiSCAPE & 74 & 0.86 &  0.23 \\
& Fe & BiSCAPE & ... & 0.54 & ... \\
& Cu & BiSCAPE & ... & 0.70 & ... \\
& Zn & BiSCAPE & ... & 0.42 & ... \\
\bottomrule
\end{tabular}
\label{tab:my_label}
\end{table}

@@

%%% --- Figure. Comparison between measurements and predictions values in the test dataset --- %%%
% Put the figure text closer to the Figure 3
\captionsetup[figure]{skip=6pt}
% We add the figure with the study domain 
\begin{figure}[!htb]
\includegraphics[width=1.0\textwidth]{figures/lur_map_plot.png}
\caption{Pregnancy exposure for the entire pregnancy period \textit{NO$_2$}, \textit{PM$_{2.5}$}, \textit{BC}.}
\label{fig2}
\end{figure}
